Component response rate variation drives stability in large complex systems

### 2018-05-26 notebook/SI.Rmd
Update SI

```{r, echo = FALSE}
source(file = "R/sim_mat.R");
source(file = "R/plot_figs.R");
```

@@

**Note: All code and data are publicly available on [GitHub](https://github.com/bradduthie/random_matrix_stability)**

@@

```{r, echo = TRUE}
load(bi_pr_st);
pr_st  <- bi_pr_st[,-1];
```

@@

```{r, echo = FALSE}
dat <- read.csv(file = "sim_results/C_1/random_all.csv");
dat <- dat[,-1];
```

@@

This function was applied to all created matrices $M$, then the number of stable $M$ matrices was estimated [exactly as it was](#Incr_S) in the main text for random matrices for values of $S$ from 2 to 50 (100 in the case of the relatively more stable predator-prey interactions), except that only 100000 random $M$ were generated instead of 1 million. The following tables for restricted ecological communities can therefore be compared with the random $M$ [results above](#Incr_S). As with the [results above](#Incr_S), in the tables below, `A0` refers to matrices when $\gamma = 1$ and `A1` refers to matrices after $Var(\gamma)$ is added. The column `A0_unstable` shows the number of `A0` matrices that are unstable, and the column `A0_stable` shows the number of `A0` matrices that are stable (these two columns sum to 100000). Similarly, the column `A1_unstable` shows the number of `A1` matrices that are unstable and `A1_stable` shows the number that are stable. The columns `A1_stabilised` and `A1_destabilised` show how many `A0` matrices were stabilised or destabilised, respectively, by $Var(\gamma)$.

@@

@@

```{r, echo = FALSE}
C3dat   <- read.csv(file = "sim_results/C_other/rand_c-0pt3.csv");
C3dat   <- C3dat[,-1];
C3d_tab <- C3dat[,1:7];
kable(C3d_tab);
```

@@

```{r, echo = FALSE}
C5dat   <- read.csv(file = "sim_results/C_other/rand_c-0pt5.csv");
C5dat   <- C5dat[,-1];
C5d_tab <- C5dat[,1:7];
kable(C5d_tab);
```

@@

```{r, echo = FALSE}
C7dat   <- read.csv(file = "sim_results/C_other/rand_c-0pt7.csv");
C7dat   <- C7dat[,-1];
C7d_tab <- C7dat[,1:7];
kable(C7d_tab);
```

@@

```{r, echo = FALSE}
C9dat   <- read.csv(file = "sim_results/C_other/rand_c-0pt9.csv");
C9dat   <- C9dat[,-1];
C9d_tab <- C9dat[,1:7];
kable(C9d_tab);
```

>>>>

```{r, echo = FALSE}
source(file = "R_old/sim_mat.R");
source(file = "R_old/plot_figs.R");
```

**Note: All text, code, and data underlying this manuscript are publicly available on [GitHub](https://github.com/bradduthie/random_matrix_stability) as part of the RandomMatrixStability package**. The text below explains how all results from the main manuscript can be recreated using the RandomMatrixStability package available on [GitHub](https://github.com/bradduthie/random_matrix_stability). To download this package, which includes all functions and tools for recreating the text, this supplemental information, and running all code, the [`devtools` library](https://cran.r-project.org/web/packages/devtools/index.html) is needed.

```{r, eval = FALSE}
install.packages("devtools");
library(devtools);
```

The code below installs the RandomMatrixStability package using devtools.

```{r, eval = FALSE}
install_github("bradduthie/random_matrix_stability")
```

While downloading this package is recommended, all relevant code is also reproduced below with explanation.

@@

@@

The above functions produced the `bi_pr_st` data.

```{r, echo = TRUE}
data(bi_pr_st);
pr_st  <- bi_pr_st[,-1];
```

@@

Figure 3 of the main text reports the number of stable random complex systems found over 1 million iterations. The data used to make this figure is read into R below.

```{r, echo = TRUE}
dat <- data(random_all);
dat <- dat[,-1]; # Extra row indicating column removed
```

@@

This function was applied to all created matrices $M$, then the number of stable $M$ matrices was estimated [exactly as it was](#Incr_S) in the main text for random matrices for values of $S$ from 2 to 50 (100 in the case of the relatively more stable predator-prey interactions), except that only 100000 random $M$ were generated instead of 1 million. This produced the data set below.

The following tables for restricted ecological communities can therefore be compared with the random $M$ [results above](#Incr_S). As with the [results above](#Incr_S), in the tables below, `A0` refers to matrices when $\gamma = 1$ and `A1` refers to matrices after $Var(\gamma)$ is added. The column `A0_unstable` shows the number of `A0` matrices that are unstable, and the column `A0_stable` shows the number of `A0` matrices that are stable (these two columns sum to 100000). Similarly, the column `A1_unstable` shows the number of `A1` matrices that are unstable and `A1_stable` shows the number that are stable. The columns `A1_stabilised` and `A1_destabilised` show how many `A0` matrices were stabilised or destabilised, respectively, by $Var(\gamma)$.

@@

All data reported below for various values of $C$ are accessible using the below.

```{r}
data(connectedness);
```

This includes the objects `C3dat`, `C5dat`, `C7dat`, and `C9dat`, which includes the results for $C = 0.3$, $C = 0.5$, $C = 0.7$, and $C = 0.9$, respectively.

@@

```{r, echo = FALSE}
C3dat   <- C3dat[,-1];
C3d_tab <- C3dat[,1:7];
kable(C3d_tab);
```

@@

```{r, echo = FALSE}
C5dat   <- C5dat[,-1];
C5d_tab <- C5dat[,1:7];
kable(C5d_tab);
```

@@

```{r, echo = FALSE}
C7dat   <- C7dat[,-1];
C7d_tab <- C7dat[,1:7];
kable(C7d_tab);
```

@@

```{r, echo = FALSE}
C9dat   <- C9dat[,-1];
C9d_tab <- C9dat[,1:7];
kable(C9d_tab);
```
